
age <- c( 
Patient_01 = 23, Patient_02 = 67, Patient_03 = 41, Patient_04 = 58, Patient_05 = 34, Patient_06 = 72, Patient_07 = 29, Patient_08 = 46, Patient_09 = 81, Patient_10 = 19 
)
fev1 <- c(
  Patient_01 = 85,
  Patient_02 = 62,
  Patient_03 = 45,
  Patient_04 = 91,
  Patient_05 = 38,
  Patient_06 = 70,
  Patient_07 = 55,
  Patient_08 = 76,
  Patient_09 = 49,
  Patient_10 = 88
)
```{r}
sum(age < 40) #age<40 will produce a logical vector automatically, and TURE=1, FALSE=0
#sum(age < 40)        # 小于 40 岁的人数
sum(age >= 60)       # 60 岁及以上人数
mean(age < 40)       # 小于 40 岁的比例
which(age < 40)      # 找出满足条件者的位置
age[age < 40]        # 取出所有小于 40 岁的年龄
names(age)[age < 40] # 取出这些患者的名字
```
Create a logical vector indicating which patients have reduced lung function (FEV1 < 70), then print the IDs of those patients
```{r}
reduced_logical <- fev1 <70
reduced_logical
print(names(fev1)[reduced_logical]) #The logical vector can be used as index too, R will automatically save TRUE one by one
# names(reduced_logical)[TRUE],TRUE is an element with a length of one, so R will recycle it. 
```
How could I write an if statement that prints “Reduced lung function” if patient 2 has an FEV1 less than 70?
if (fev1["Patient_02"]) {
  print("Reduced lung function")
```{r}
if(fev1["Patient_02"]<70){print("Reduced lung function")}
```
Write a series of expressions that categorize Patient 02's FEV1 as:
"Healthy" if FEV1 is greater than 80 
"Moderate impairment" if FEV1 between 60 and 80 
"Poor" if FEV1 is between 40 and 60 
"Very poor" if FEV1 is less than 40
```{r}
if(fev1["Patient_02"]>80){ #neat writing:{end,}beginning
  print("Healthy")
}else if(fev1["Patient_02"]>60){ #don't need to write<=80
  print("Moderate impairment")
}else if(fev1["Patient_02"]>40){
  print("Poor")
}else{print("Very poor")}
```
Go through every patient’s FEV1 and print:
"Healthy" if FEV1 is greater than 80 
"Moderate impairment" if FEV1 between 60 and 80 
"Poor" if FEV1 is between 40 and 60 
"Very poor" if FEV1 is less than 40


Now modify the loop to print something like:Patient_01: HealthyPatient_02: Moderate
```{r}
# for (patient_id in names(fev1)){
#   for(patient in fev1){
#     if(patient>80){
#       print(paste(patient_id,"Healthy"))
#       }else if(patient>60){
#         print(paste(patient_id,"Moderate impairment"))
#         }else if(fev1["Patient_02"]>40){
#           print(paste(patient_id,"Poor"))
#           }else{print(paste(patient_id,"Very poor"))}
#   }
# }

for (patient_id in names(fev1)){
  if(fev1[patient_id]>80){
    print(paste0(patient_id,": Healthy"))
    }else if(fev1[patient_id]>60){
      print(paste0(patient_id,": Moderate impairment"))
      }else if(fev1[patient_id]>40){
        print(paste0(patient_id,": Poor"))
      }else{print(paste0(patient_id,": Very poor"))}
  }
```


Loops are often used to generate new variablesThe general approach:
Create an empty object before the loop 
Update the object during each iteration 
Store the result for every observation
Practice:
Using the age vector, write a loop that creates a character vector containing:
"over 30" if the patient is older than 30 
"under 30" if the patient is 30 or younger 
The final vector should have the same length as age.
```{r}
for(patient_id in names(age)){
  if(age[patient_id]>30){
    print(paste(patient_id,": over 30","age=",age[patient_id]))
  }else{
    print(paste(patient_id,": is 30 or younger","age=",age[patient_id]))
  }
}
```
Write a for loop that:
Prints the age and FEV1 of each participant 
Keeps a running total of participant ages 
Stops the loop once the cumulative age exceeds 150 

Example output:
Patient_01: age = 23, FEV1 = 99
Patient_02: age = 88, FEV1 = 14
Patient_03: age = 55, FEV1 = 72
```{r}
cum_age <- 0  #vector can only add with a vector
for(patient_id in names(age)){
  print(paste0(patient_id,": age = ",age[patient_id],", FEV1 = ",fev1[patient_id]))
  cum_age <- cum_age + age[patient_id]
  if(cum_age > 150){
    break
  }
}
  

```
