---
title: "Functions"
output: html_document
---

BC Children’s Hospital
```{r}
fev1_bcch <- c(
  Patient_01 = 85,
  Patient_02 = 62,
  Patient_03 = 45,
  Patient_04 = 91,
  Patient_05 = 38,
  Patient_06 = 70,
  Patient_07 = 55,
  Patient_08 = 76,
  Patient_09 = 49,
  Patient_10 = 88
)
age_bcch <- c(
  Patient_01 = 23,
  Patient_02 = 62,
  Patient_03 = 45,
  Patient_04 = 91,
  Patient_05 = 38,
  Patient_06 = 70,
  Patient_07 = 55,
  Patient_08 = 76,
  Patient_09 = 49,
  Patient_10 = 88
)
```
Using the BCCH data, write a loop that creates a character vector called risk_bcch containing a risk classification for each patient.
Assign patients as:
"High risk" if: 
Age is greater than 50 and 
FEV1 is less than 70 
"Moderate risk" if: 
Age is greater than 30 or 
FEV1 is less than 70 
"Low risk" otherwise 
The final vector should:
Have the same length as the input data 
Use patient IDs as names
```{r}
risk_bcch <- c(for(id in names(age_bcch)){
  if(age_bcch[id]>50 & fev1_bcch < 70){id = "High risk"}
})
risk_bcch
```