---
title: "Programming Assignment 1"
output: html_document
---

Complete all questions by filling in the code chunks.

This assessment will test your ability to work with vectors, logical operators, and loops in R.

```{r setp, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
```

---

# Question 1 (3 points)

Amrit got a grade of **80%** on his exam. Sam got a grade of **90%** on his exam.

Replace the `NA` values with the correct answers.

1. Create a variable called `amrit` and assign Amrit's grade.
2. Create a variable called `sam` and assign Sam's grade.
3. Use the built-in `mean()` function to calculate their average grade.

```{r question-1}
# Define a variable for Amrit's grade
amrit <- NA
amrit <- 80

# Define a variable for Sam's grade
sam <- NA
sam <- 90

# Calculate the average grade
avg <- mean(c(NA, NA))
avg <- mean(c(amrit,sam))
print(paste0("Amrit's grade is ", amrit,"%"))
print(paste0("Sam's grade is ", sam,"%"))
print(paste0("The mean grade is ", avg,"%"))
```

---

# Load the Sample Data

Use the following vector of results from a biology course quiz for all questions going forward. Each value represents the quiz score for one student. You will use R to summarize the results and classify student performance.

```{r load-data}
scores <- c(
  Alice = 88,
  Ben = 73,
  Chloe = 95,
  Daniel = 61,
  Emma = 42,
  Finn = 79,
  Grace = 84,
  Henry = 56,
  Isla = 91,
  Jack = 67
)
```
---


# Question 2 (3 points)

How many students scored **80 or higher**?

```{r question-2}
sum(scores >= 80)
```

---

# Question 3 (3 points)

How many students scored **between 60 and 80 (inclusive)**?

```{r question-3}
sum( 60 <= scores & scores <= 80)
```

---

# Question 4 (3 points)

Create a logical vector called `passed` that is `TRUE` for students with a score of **50 or higher**.

Then print the names of the students who passed.

```{r question-4}
passed <- scores >= 50
print(names(passed))
```

---

# Question 5 (3 points)

Write a `for` loop that prints every score.

Example output:

```
88
73
95
...
```

```{r question-5}

for(student in scores){
  print(student)
}
```

---

# Question 6 (3 points)

Fill in the `...` with the correct answer.

Write a `for` loop that prints:

- `"Pass"` if the score is **50 or higher**
- `"Fail"` otherwise

Example output:

```
Pass
Pass
Pass
Fail
...
```

```{r question-6}
for (student in scores) {
  if (student >= 50) {
    print("Pass")
  } else {
    print("Fail")
  }
}
```

---

# Question 7 (3 points)

Fill in the `...` with the correct answer.

Modify your previous loop so that it prints the student's name as well.

Example output:

```
Alice: Pass
Ben: Pass
Emma: Fail
...
```

```{r question-7}
for (id in names(scores)) {
  if (scores[id] > 50) {
    print(paste0(id, ": Pass"))
  } else {
    print(paste0(id, ": Fail"))
  }
}
```


---

# BONUS - Question 8 (3 points)

Write a `for` loop that:

- Prints each student's name, score and whether they passed.
- Keeps a running total of all scores.
- Stops once the running total is greater than **350**.

Expected output:
```
Alice: 88 (Pass)
Ben: 73 (Pass)
Chloe: 95 (Pass)
Daniel: 61 (Pass)
Emma: 42 (Fail)
```

```{r bonus-question}
total_score <- 0
for(id in names(scores)){if (scores[id] > 50) {
    print(paste0(id, ": ",scores[id]," (Pass)"))
  } else {
    print(paste0(id, ": ",scores[id]," (Fail)"))
  }
  total_score <- total_score + scores[id]
  if(total_score > 350){
    break
  }
}
```
