---
title: "Programming Assignment 2"
output: html_document
---

Complete all questions by filling in the code chunks.

This assessment will test your ability to work with `dplyr` for data manipulation and `ggplot2` for plotting.

```{r setp, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
```

---

# Setup

Run the two cells below before starting the assessment.

```{r libraries}
library(ggplot2)
library(dplyr)

```

```{r load-data}
flowers <- iris
head(flowers)
```

---

# Question 1 (3 points)

How many observations (rows) are in the dataset?

```{r question-1}
nrow(flowers)
```

---

# Question 2 (3 points)

Display only the flowers that belong to the species `"setosa"`.

```{r question-2}
flowers %>%
  filter(Species=="setosa")
```

---

# Question 3 (3 points)

Create a new column called `PetalSize`.

A flower should be classified as:

- `"Large"` if `Petal.Length` is **greater than or equal to 5**
- `"Small"` otherwise.

```{r question-3}
flowers %>%
  mutate(
    PetalSize = ifelse(Petal.Length >= 5,"Large","Small")
  )
```

---

# Question 4 (3 points)

Calculate the **average Sepal.Length** for each species.

```{r question-4}
flowers %>%
  group_by(Species) %>%
  summarise(
    MeanSepalLength = mean(Sepal.Length)
  )
```

---

# Question 5 (3 points)

Complete the pipeline below.

Display only the columns:

- `Species`
- `Sepal.Length`
- `Petal.Length`

Then arrange the rows from **smallest Petal.Length to largest**.

```{r question-5}
flowers %>%
  select("Species","Sepal.Length","Petal.Length") %>%
  arrange(Petal.Length)
```

---

# Question 6 (3 points)

Complete the code below to produce a scatterplot.

- x-axis: `Sepal.Length`
- y-axis: `Petal.Length`

```{r question-6}
ggplot(flowers, aes(x = Sepal.Length, y = Petal.Length)) +
  geom_point()
```

---

# Question 7 (3 points)

Modify the plot from Question 6 so that:

- Points are coloured by `Species`
- Add a title: `"Sepal Length vs Petal Length"`
- Label the x-axis `"Sepal Length (cm)"`
- Label the y-axis `"Petal Length (cm)"`

```{r question-7}
ggplot(flowers, aes(x = Sepal.Length, y = Petal.Length, colour = Species)) +
  geom_point() +
  labs(
    title = "Sepal Length vs Petal Length",
    x = "Sepal Length (cm)",
    y = "Petal Length (cm)"
  )
```

---

# BONUS - Question 8 (3 points)

Create a function called `plot_species()` that takes in a species name (e.g. `"setosa"`) and creates a customized scatterplot using only flowers from that species.

The function should:

- Filter the dataset to include only the selected species
- Create a scatterplot showing:
  - Sepal length on the x-axis
  - Petal length on the y-axis
- Color points based on petal width
- Scale point size based on sepal width
- Add a smooth trend line (try ?geom_smooth)
- Add a title that dynamically includes the species name
- Add informative axis labels

Your function should work for all three species. Make sure to add proper function documentation.

```{r bonus-question}
plot_species <- function(FlowerName) {
  filtered_flowers = filter(flowers,Species==FlowerName)
ggplot(filtered_flowers, aes(x = Sepal.Length, y = Petal.Length, colour = Petal.Width)) +
  geom_point() +
  geom_smooth() +
  labs(
    title =paste0("Category Color by Petal Width in ", FlowerName),
    x = "Sepal Length (cm)",
    y = "Petal Length (cm)"
  )
}

# Test your function
print(plot_species("setosa"))
print(plot_species("versicolor"))
print(plot_species("virginica"))
```
test
```{r}
?geom_smooth
```
```
